\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}


%====================
% EXPERIENCE C
%====================
\subsection{{Graduate Teaching Assistant \hfill January 2022 --- May 2022}}
\subtext{Appalachain State University \hfill Boone, NC}
\begin{zitemize}
\item Assigned three classes to assist teaching.
\item Responsibilities included tutoring, grading papers, in class/lab assistance.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{CS4All \hfill May 2021 --- August 2021}}
\subtext{Appalachain State University \hfill Boone, NC}
\begin{zitemize}
\item A part of the CS4App team.
\item Our mission was to assist public school teachers with learning how to code in (Snap/Scratch) coding languages.
\item Tasks: Write up Scratch/Snap assignments/instructions that are easy to read and understand.
\item Tasks: Find useful artificial intelligence resources for the teachers to use in the classroom to help students explore the machine learning field
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Sales Representative \hfill April 2019 --- Present}}
\subtext{Eddie Bower/Boone's Fly Shop/Foseco Fishing CO \hfill Boone/Asheville, NC}
\begin{zitemize}
\item Throughout the past few years I have had several retail positions.
\item Titles have been from sales representative to lower management.
\item Responsibilities included, making sales, store upkeep, opening/closing store.
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{ELECTRICIAN’S ASSISTANT \hfill June 2018 --- August 2018}}
\subtext{BUNCOMBE COUNTY SCHOOL SYSTEM \hfill Asheville, NC}
\begin{zitemize}
\item I was a part of a special team assigned to a county wide electoral project
\item Engaged in electrical work and manual labor
\item Gained introductory level electrical knowledge
\item Saving the county 3-months of time on a 12-month long project.
\end{zitemize}


%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}